Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-05 2020/JPDC_MCO/2020_JPDC.tex
1. исправил благодарность

\section*{Acknowledgements} 
This research was supported by the Russian Science Foundation, project No 16-11-10150 ``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''

>>>>

\section*{Acknowledgements} 
The work was supported by the Ministry of Science and Higher Education of the Russian Federation, agreement No 075-15-2020-808
